---
title: "Yield_Climate"
author: "Zhehan"
date: "11/28/2020"
output: html_document
---

#Package
```{r}
library(ggplot2)
library(gridExtra)
library(tidyr)
library(raster)
library(sp)
library(readxl)
library(lubridate)
library(RColorBrewer)
library(corrplot)
library(caret)
```
#CA_County
```{r}
path_shp <- "C:/Users/tangz/Box Sync/Tomato_Phenology_RemoteSensing/Shapefiles"
CA_County <- shapefile(file.path(path_shp, "CA_Counties_TIGER2016.shp"))
tomato_fidbound_2013_gee <- shapefile(file.path(path_shp, "tomato_fidbound_2013_gee.shp"))
plot(CA_County)
head(CA_County@data)
CA_County@data <- CA_County@data[,c(5,16,17)]
CA_County@data

#Output
crs(tomato_fidbound_2013_gee)
CA_County_GEE <- spTransform(CA_County, crs(tomato_fidbound_2013_gee))
crs(CA_County_GEE)
shapefile(CA_County_GEE,file.path(path_shp, "CA_County_GEE.shp"),overwrite=  TRUE)
```


#Read Yield data from NASS USDA
```{r}
path_NASS <- "C:/Users/tangz/Box Sync/Tomato_Phenology_RemoteSensing/Historic_Yield_Data/NASS"
yield_county_nass <- read.csv(file.path(path_NASS, "Tomato_Processing_Harvested.csv"))
head(yield_county_nass)

#clean the dataset 
yield_county_nass <- yield_county_nass[,c("Year","State","County","Value")]
head(yield_county_nass)
unique(yield_county_nass$State)
yield_county_nass <- subset(yield_county_nass, State=="CALIFORNIA")
unique(yield_county_nass$County)

ggplot(yield_county_nass, aes(x = Year, y = Value, color = County)) + geom_point() + geom_line() + theme_bw()
ggplot(subset(yield_county_nass, County!="OTHER (COMBINED) COUNTIES" & Year>2007), aes(x = Year, y = Value, color = County)) + geom_point() + theme_bw() + facet_wrap(~County)

```

#Read Yield data from annual report 
```{r}
path_report <- "C:/Users/tangz/Box Sync/Tomato_Phenology_RemoteSensing/Historic_Yield_Data/Annual_Report"
yield_county_report <- read_excel(file.path(path_report, "Processing Tomato Yield.xlsx"), sheet = 1, skip = 2)
yield_county_report <- gather(yield_county_report, Year, Yield, '1999':'2019')
head(yield_county_report)
names(yield_county_report)[1] <- "County"

ggplot(yield_county_report, aes(x  = Year, y = Yield, color = County)) + geom_point() + theme_bw()

totyield_county_report <- read_excel(file.path(path_report, "Processing Tomato Yield.xlsx"), sheet = 2, skip = 2)
totyield_county_report <- gather(totyield_county_report, Year, TotalYield, '1999':'2019')
names(totyield_county_report)[1] <- "County"
head(totyield_county_report)

#combine 
yield_county_report <- base::merge(totyield_county_report,yield_county_report,by = c("County","Year"))
head(yield_county_report)

#add area 
yield_county_report$Area <- yield_county_report$TotalYield/yield_county_report$Yield

#change class
str(yield_county_report)
yield_county_report$Year <- as.numeric(yield_county_report$Year)

ggplot(subset(yield_county_report, Year >=2010), aes(x = Year, y = Yield, color = County)) + geom_point() + theme_bw() + facet_wrap(~County) + ylim(30,70) + scale_x_continuous(breaks = c(2010, 2014, 2018))
ggplot(subset(yield_county_report, Year > 2007), aes(x = Year, y = Yield, color = County)) + geom_point() + theme_bw() + facet_wrap(~County) + ylim(30,70) + scale_x_continuous(breaks = c(2010, 2014, 2018)) + ylab("Yield (tons/acre)")


ggplot(subset(yield_county_nass, County!="OTHER (COMBINED) COUNTIES" & Year>2007 & County != "BUTTE"), aes(x = Year, y = Value, color = County)) + geom_point() + theme_bw() + facet_wrap(~County) + ylim(30,70) + scale_x_continuous(breaks = c(2010, 2014, 2018))

```

#Read Weather data from Daymet
```{r}
path_daymet <- "D:/Tomato_Phenology_RemoteSensing/GEE_output/Daymet"
list.files(path_daymet)
maxtemp_county <- read.csv(file.path(path_daymet, "CA_county_maxtemp_2.csv"))
mintemp_county <- read.csv(file.path(path_daymet, "CA_county_mintemp_2.csv"))
#subset
maxtemp_county <- maxtemp_county[,c(4:6)]
mintemp_county <- mintemp_county[,c(4:6)]
dim(maxtemp_county)  #20880, 3
dim(mintemp_county) #20880, 3
names(maxtemp_county) <- c("County","MaxTemp","Time")
names(mintemp_county) <- c("County","MinTemp","Time")
identical(maxtemp_county$County, mintemp_county$County)
identical(maxtemp_county$Time, mintemp_county$Time)
#merge 
daymet_county <- merge(maxtemp_county, mintemp_county, by = c("County","Time"))
dim(daymet_county) #20880,4
#change Time column
daymet_county$Time <- strptime(as.character(daymet_county$Time), format = "%Y-%m-%d")
#add year and month
daymet_county$Year <- year(daymet_county$Time)
daymet_county$Month <- month(daymet_county$Time)
dim(daymet_county) #20880,5
#remove time 
daymet_county$Time <- NULL
#long  to wide
daymet_county_wide <- tidyr::pivot_wider(daymet_county, names_from = Month, values_from = MaxTemp:MinTemp)
daymet_county_wide
dim(daymet_county_wide)  #1740,26
names(daymet_county_wide)


```

#Combine the yield with the weather data
```{r}
head(yield_county_report)
head(daymet_county)
dim(yield_county_report) #252,4
dim(daymet_county_wide) #1740, 26
yield_daymet_county <- merge(yield_county_report, daymet_county_wide, by = c("County","Year"))
dim(yield_daymet_county)  #252, 28
#remove the NAs 
sum(is.na(yield_daymet_county)) #28 NAs
yield_daymet_county <- na.omit(yield_daymet_county)
dim(yield_daymet_county) #238, 29
#change the classes
str(yield_daymet_county)
yield_daymet_county$County <- as.factor(yield_daymet_county$County)
yield_daymet_county$Year <- as.numeric(yield_daymet_county$Year)
dim(yield_daymet_county) #238,29
```

##Exploratory Analysis of the county-level data
```{r}
ggplot(yield_daymet_county, aes(x = Year, y = Yield)) + geom_point(aes(color = County)) + theme_bw() + geom_smooth(method = "lm")
ggplot(yield_daymet_county, aes(x = Year, y = Yield, color = County)) + geom_point() + theme_bw() + geom_smooth(method = "lm", se = FALSE)
sum(yield_daymet_county$Yield>65) #1
#remove one outlier 
yield_daymet_county <- subset(yield_daymet_county, Yield < 65)
dim(yield_daymet_county) #237,28

par(mfrow = c(2,3))
for(i in 1:24){
  plot(x = yield_daymet_county[,i+4], y = yield_daymet_county$Yield, xlab = names(yield_daymet_county)[i+4], ylab = "Yield")
}
```

#State weighted Average
```{r}
yield_daymet_state <- data.frame(matrix(0, nrow = 21, ncol = 28))
names(yield_daymet_state) <- names(yield_daymet_county)[2:29]
yield_daymet_state
yield_daymet_state$Year <- unique(yield_daymet_county$Year)


yield_daymet_state[,c(1,2,4)] <- aggregate(yield_daymet_county[,c('TotalYield','Area')], by = list("Year"=yield_daymet_county$Year), sum)
yield_daymet_state$Yield <- yield_daymet_state$TotalYield/yield_daymet_state$Area
for(i in 1999:2019){
  df <- subset(yield_daymet_county, Year ==i)
  df$weight <- df$Area/sum(df$Area)
  for(j in 1:24){
    yield_daymet_state[i-1998,j+4] <- weighted.mean(x = df[,j+5], w = df$weight)
  }
}
yield_daymet_state
```
##Exploratory plots
```{r}
ggplot(yield_daymet_state, aes(x = Year, y = Yield)) + geom_point() + theme_bw() + geom_smooth(method = "lm") + ylab("Yield (tons/acre)") + ggtitle("State average Yield vs Year")

```

#Follow the methods applied by Lobell
##Remove the impact of technology trends
###Fit a linear trend to yield time series
```{r}
#county level 
lm_tech <- lm(Yield~Year, data = yield_daymet_county)
par(mfrow = c(1,1))
#plot(lm_tech)
summary(lm_tech) #R2 = 0.4982, p<2e-16
yield_daymet_county$Yield_tech <- yield_daymet_county$Yield-predict(lm_tech, data = yield_daymet_county$Year)
ggplot(yield_daymet_county, aes(x = Year, y = Yield_tech)) + geom_point(aes(color = County)) + theme_bw() + ylab("Technology-adjusted Yield") + geom_smooth(method = "loess")

#state level
lm_tech_state <- lm(Yield~Year, data =yield_daymet_state)
summary(lm_tech_state)  #R2 = 0.8316
yield_daymet_state$Yield_tech <- yield_daymet_state$Yield -  predict(lm_tech_state, data = yield_daymet_state$Year)
ggplot(yield_daymet_state, aes(x = Year, y = Yield_tech)) + geom_point() + theme_bw() + ylab("Technology-adjusted Yield (tons/acre)") + geom_smooth(method = "loess")

```


##Univariable regression 
###State level
```{r}
r2_lm2_yield_daymet_state <- data.frame("Variable"=names(yield_daymet_state)[5:28],"r2"=0,"p-value"=0)
for(i in 1:24){
  lm2_yield_daymet_state <- lm(yield_daymet_state$Yield_tech~yield_daymet_state[,i+4]+I(yield_daymet_state[,i+4]^2))
  r2_lm2_yield_daymet_state[i,2] = summary(lm2_yield_daymet_state)$r.squared
  r2_lm2_yield_daymet_state[i,3] = summary(lm2_yield_daymet_state)$coefficients[2,4]
  
}


View(r2_lm2_yield_daymet_state)

head(r2_lm2_yield_daymet_state)
r2_lm2_yield_daymet_state$MaxMin <- as.factor(substr(as.character(r2_lm2_yield_daymet_state$Variable), start = 1, stop = 3))
r2_lm2_yield_daymet_state$Month <- as.integer(sub('.*_','',r2_lm2_yield_daymet_state$Variable))

```
####Plots
```{r}
#R2 change
ggplot(r2_lm2_yield_daymet_state, aes(x = Month, y = r2)) + geom_line(aes(linetype = MaxMin), size = 2)+ theme_bw() + ylim(0,0.5) + ylab("R2") + scale_x_continuous(breaks = 1:12) + theme(legend.title = element_blank()) + ggtitle("State-level detrend Yield vs Weather Variables")

#Yield vs Weather
ggplot(yield_daymet_state, aes(x =  MaxTemp_7, y = Yield_tech)) + geom_point() + theme_bw() + geom_smooth(method = "lm", formula = y~x+I(x^2), se = FALSE) + xlab("July Tmax")
ggplot(yield_daymet_state, aes(x =  MaxTemp_4, y = Yield_tech)) + geom_point() + theme_bw() + geom_smooth(method = "lm", formula = y~x+I(x^2), se = FALSE) + xlab("April Tmax")
ggplot(yield_daymet_state, aes(x =  MaxTemp_7, y = Yield_tech)) + geom_point(aes(color = Year)) + theme_bw() + geom_smooth(method = "lm", formula = y~x+I(x^2), se = FALSE) + xlab("July Tmax") + scale_color_continuous(type = "viridis")
ggplot(yield_daymet_state, aes(x =  MaxTemp_4, y = Yield_tech)) + geom_point(aes(color = Year)) + theme_bw() + geom_smooth(method = "lm", formula = y~x+I(x^2), se = FALSE) + xlab("April Tmax") + scale_color_continuous(type = "viridis")
ggplot(yield_daymet_state, aes(x =  MinTemp_10, y = Yield_tech)) + geom_point(aes(color = Year)) + theme_bw() + geom_smooth(method = "lm", formula = y~x+I(x^2), se = FALSE) + xlab("October Tmin") + scale_color_continuous(type = "viridis")


#Yield-tech trend 
p1 = ggplot(yield_daymet_state, aes(x =  Year, y = Yield_tech)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("detrended Yield")
p2 = ggplot(yield_daymet_state, aes(x =  Year, y = MaxTemp_7)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("July Tmax")
grid.arrange(p1,p2, nrow =2)

p1 = ggplot(yield_daymet_state, aes(x =  Year, y = Yield_tech)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("detrended Yield")
p2 = ggplot(yield_daymet_state, aes(x =  Year, y = MaxTemp_4)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("April Tmax")
grid.arrange(p1,p2, nrow =2)

p1 = ggplot(yield_daymet_state, aes(x =  Year, y = Yield_tech)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("detrended Yield")
p2 = ggplot(yield_daymet_state, aes(x =  Year, y = MinTemp_10)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("October Tmin")
grid.arrange(p1,p2, nrow =2)

#Correlation 
cor_yield_daymet_state_1 <- cor(x = yield_daymet_state[,5:16], y = yield_daymet_state[,17:28])
corrplot(cor_yield_daymet_state_1)
cor_yield_daymet_state_2 <- cor(x = yield_daymet_state[,5:16], y = yield_daymet_state[,5:16])
corrplot.mixed(cor_yield_daymet_state_2)
cor_yield_daymet_state <- cor(yield_daymet_state)
```


###County level 
```{r}
r2_lm2_yield_daymet <- data.frame("Variable"=names(yield_daymet)[5:28],"r2"=0,"p-value"=0)
for(i in 1:24){
  lm2_yield_daymet <- lm(yield_daymet$Yield_tech~yield_daymet[,i+4]+I(yield_daymet[,i+4]^2))
  r2_lm2_yield_daymet[i,2] = summary(lm2_yield_daymet)$r.squared
  r2_lm2_yield_daymet[i,3] = summary(lm2_yield_daymet)$coefficients[2,4]
  
}
View(r2_lm2_yield_daymet)

head(r2_lm2_yield_daymet)
r2_lm2_yield_daymet$MaxMin <- as.factor(substr(as.character(r2_lm2_yield_daymet$Variable), start = 1, stop = 3))
r2_lm2_yield_daymet$Month <- as.integer(sub('.*_','',r2_lm2_yield_daymet$Variable))


```

####Plots
```{r}
#R2 change
ggplot(r2_lm2_yield_daymet, aes(x = Month, y = r2)) + geom_line(aes(linetype = MaxMin), size = 2)+ theme_bw() + ylim(0,0.5) + ylab("R2") + scale_x_continuous(breaks = 1:12) + theme(legend.title = element_blank()) + ggtitle("State-level detrend Yield vs Weather Variables")

#Yield vs Weather
ggplot(yield_daymet_county, aes(x =  MaxTemp_8, y = Yield_tech)) + geom_point(aes(color = Year)) + theme_bw() + geom_smooth(method = "lm", formula = y~x+I(x^2), se = FALSE) + xlab("August Tmax")+scale_color_continuous(type = "viridis")
ggplot(yield_daymet_county, aes(x =  MinTemp_5, y = Yield_tech)) + geom_point(aes(color = Year)) + theme_bw() + geom_smooth(method = "lm", formula = y~x+I(x^2), se = FALSE) + xlab("May Tmin")+scale_color_continuous(type = "viridis")
ggplot(yield_daymet_county, aes(x =  MinTemp_12, y = Yield_tech)) + geom_point(aes(color = Year)) + theme_bw() + geom_smooth(method = "lm", formula = y~x+I(x^2), se = FALSE) + xlab("December Tmin")+scale_color_continuous(type = "viridis")



#Yield-tech trend 
p1 = ggplot(yield_daymet_county, aes(x =  Year, y = Yield_tech)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("detrended Yield")
p2 = ggplot(yield_daymet_county, aes(x =  Year, y = MaxTemp_7)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("July Tmax")
grid.arrange(p1,p2, nrow =2)

p1 = ggplot(yield_daymet_county, aes(x =  Year, y = Yield_tech)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("detrended Yield")
p2 = ggplot(yield_daymet_county, aes(x =  Year, y = MaxTemp_4)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("April Tmax")
grid.arrange(p1,p2, nrow =2)

p1 = ggplot(yield_daymet_county, aes(x =  Year, y = Yield_tech)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("detrended Yield")
p2 = ggplot(yield_daymet_county, aes(x =  Year, y = MinTemp_10)) + geom_point()+theme_bw()+geom_smooth(method = "loess", se = FALSE) + ylab("October Tmin")
grid.arrange(p1,p2, nrow =2)

#Correlation 
cor_yield_daymet_1 <- cor(x = yield_daymet_county[,5:16], y = yield_daymet_county[,17:28])
corrplot(cor_yield_daymet_1)
cor_yield_daymet_2 <- cor(x = yield_daymet_county[,5:16], y = yield_daymet_county[,5:16])
corrplot.mixed(cor_yield_daymet_2)
cor_yield_daymet <- cor(yield_daymet_county)
```

##Multivariable regression 
###State-level
####Tmax_7 and Tmax_4
```{r}
lm_yield_tech_daymet_state <- lm(Yield_tech~MaxTemp_7+I(MaxTemp_7^2)+MaxTemp_4+I(MaxTemp_4^2), data = yield_daymet_state)
summary(lm_yield_tech_daymet_state)
plot(y = yield_daymet_state$Yield_tech, x = predict(lm_yield_tech_daymet_state, data = yield_daymet_state), xlab = "Predicted", ylab = "Observed", xlim = c(-7,4), ylim = c(-7,4))
abline(a = 0, b =1)
cor(y = yield_daymet_state$Yield_tech, x = predict(lm_yield_tech_daymet_state, data = yield_daymet_state))^2  #0.4265
RMSE(pred = predict(lm_yield_tech_daymet_state, data = yield_daymet_state), obs = yield_daymet_state$Yield_tech)  #1.826
```
###County-level
####Tmax_7 and Tmax_4
```{r}
lm_yield_tech_daymet_county <- lm(Yield_tech~MaxTemp_7+I(MaxTemp_7^2)+MaxTemp_4+I(MaxTemp_4^2), data = yield_daymet_county)
summary(lm_yield_tech_daymet_county)
plot(y = yield_daymet_county$Yield_tech, x = predict(lm_yield_tech_daymet_county, data = yield_daymet_county), xlab = "Predicted", ylab = "Observed", xlim = c(-7,4), ylim = c(-7,4))
abline(a = 0, b =1)
cor(y = yield_daymet_county$Yield_tech, x = predict(lm_yield_tech_daymet_county, data = yield_daymet_county))^2  #0.0993
RMSE(pred = predict(lm_yield_tech_daymet_county, data = yield_daymet_county), obs = yield_daymet_county$Yield_tech)  #4.952


lm_yield_daymet_county <- lm(Yield~MaxTemp_7+I(MaxTemp_7^2)+MaxTemp_4+I(MaxTemp_4^2), data = yield_daymet_county)
summary(lm_yield_daymet_county)
plot(y = yield_daymet_county$Yield, x = predict(lm_yield_daymet_county, data = yield_daymet_county), xlab = "Predicted", ylab = "Observed")
abline(a = 0, b =1)
cor(y = yield_daymet_county$Yield, x = predict(lm_yield_daymet_county, data = yield_daymet_county))^2  #0.0993
RMSE(pred = predict(lm_yield_daymet_county, data = yield_daymet_county), obs = yield_daymet_county$Yield)  #4.952

```
####Tmax+8 and Tmin_5
```{r}
lm_yield_tech_daymet_county <- lm(Yield_tech~MaxTemp_8+I(MaxTemp_8^2)+MinTemp_5+I(MinTemp_5^2), data = yield_daymet_county)
summary(lm_yield_tech_daymet_county)
plot(y = yield_daymet_county$Yield_tech, x = predict(lm_yield_tech_daymet_county, data = yield_daymet_county), xlab = "Predicted", ylab = "Observed")
abline(a = 0, b =1)
cor(y = yield_daymet_county$Yield_tech, x = predict(lm_yield_tech_daymet_county, data = yield_daymet_county))^2  #0.170
RMSE(pred = predict(lm_yield_tech_daymet_county, data = yield_daymet_county), obs = yield_daymet_county$Yield_tech)  #4.753

lm_yield_daymet_county <- lm(Yield~MaxTemp_8+I(MaxTemp_8^2)+MinTemp_5+I(MinTemp_5^2), data = yield_daymet_county)
summary(lm_yield_daymet_county)
plot(y = yield_daymet_county$Yield, x = predict(lm_yield_daymet_county, data = yield_daymet_county), xlab = "Predicted", ylab = "Observed", xlim = c(25,65), ylim = c(25,65))
abline(a = 0, b =1)
cor(y = yield_daymet_county$Yield, x = predict(lm_yield_daymet_county, data = yield_daymet_county))^2  #0.170
RMSE(pred = predict(lm_yield_daymet_county, data = yield_daymet_county), obs = yield_daymet_county$Yield)  #4.753

```

####Nonlinear regression 
```{r}

```
#Within-Year variation 
```{r}
par(mfrow= c(1,1))
r2_lm2_yield_daymet_year <- data.frame("Year"=rep(1999:2019, each = 24),"Variable"=rep(names(yield_daymet_state)[5:28],times = 21),"r2"=0,"p-value"=0,"n"=0)

for(i in 1:21){
  df <- subset(yield_daymet_county, Year == i+1998)
  df_r2 <- subset(r2_lm2_yield_daymet_year, Year == i+1998)
  n <- nrow(df)
  for(j in 1:24){
    lm1 <- lm(df$Yield_tech~df[,j+5]+I(df[,j+5]^2))
    df_r2[j,3] <- summary(lm1)$r.squared
    df_r2[j,4] <- summary(lm1)$coefficients[2,4]
    df_r2[j,5] <- n
  }
  r2_lm2_yield_daymet_year[(1+24*(i-1)):(24+24*(i-1)),] <- df_r2
}
View(r2_lm2_yield_daymet_year)


r2_lm2_yield_daymet_year$MaxMin <- as.factor(substr(as.character(r2_lm2_yield_daymet_year$Variable), start = 1, stop = 3))
r2_lm2_yield_daymet_year$Month <- as.integer(sub('.*_','',r2_lm2_yield_daymet_year$Variable))

ggplot(subset(r2_lm2_yield_daymet_year,Year!=2019), aes(x = Month, y = r2)) + geom_line(aes(linetype = MaxMin)) + theme_bw() + ylab("R2") + scale_x_continuous(breaks = 1:12) + theme(legend.title = element_blank())+facet_wrap(~Year)

ggplot(r2_lm2_yield_daymet_state, aes(x = Month, y = r2)) + geom_line(aes(linetype = MaxMin), size = 2)+ theme_bw() + ylim(0,0.5) + ylab("R2") + scale_x_continuous(breaks = 1:12) + theme(legend.title = element_blank()) + ggtitle("State-level detrend Yield vs Weather Variables")




```


#Follow the methods applied by Zhou
```{r}
lm3 <- lm(Yield_tech~MaxTemp_7+I(MaxTemp_7^2)+MinTemp_4+I(MinTemp_4^2), data = yield_daymet_county)
summary(lm3)

lm4 <- lm(Yield_tech~MaxTemp_7+MinTemp_4^2, data = yield_daymet_county)
summary(lm4)

lm5 <- lm(Yield_tech~MaxTemp_7+I(MaxTemp_7^2), data = yield_daymet_county)
summary(lm5)

plot(x = yield_daymet_county$Yield_tech, y = yield_daymet_county$MaxTemp_7)
abline(lm5)

```

#Area comparison 
```{r}
ggplot(yield_daymet_county, aes(x = Year, y = Area, color = County)) + geom_point() + geom_line() + theme_bw()
```

